\section{Introduction}
\label{sec:intro}

Phishing remains one of the most prevalent and costly cybersecurity threats, and
automated detectors deployed across web browsers, mail gateways, and enterprise
security pipelines are a primary line of defense. A phishing verdict is also a consequential
act: marking a page as phishing drives a blocklist entry, a browser warning, or a
take-down request that pulls a live service off the web. Large language models have sharply raised the accuracy of
such detectors, reading a page's URL, Document Object Model (DOM), rendered screenshot, and certificate
to decide whether it impersonates a brand it does not own~\cite{tan2024phishllm,
li2024knowphish}. Yet accuracy is only half of what a deployment needs: the
operator who must justify a take-down and the user who sees a warning both need a
\emph{reason} they can check, and the system needs a criterion for \emph{when} a
verdict is trustworthy enough to act on without review. For a decision that can be
contested, the bottleneck is no longer whether the model is usually right, but
whether a particular verdict can be \emph{trusted and explained}.

Existing detectors approach this only indirectly. One line runs a single LLM over
the page and reports a class probability or a verbalized
confidence~\cite{tan2024phishllm}; reliability is then a property of that one
model's calibration~\cite{guo2017calibration}. A second line aggregates several
models or several samples -- self-consistency over one
model~\cite{wang2023selfconsistency}, majority voting over an
ensemble~\cite{ensembleornot2024}, or weighted label agreement in the style of
crowd-sourcing and label-free evaluation~\cite{dawid1979maximum,tci2025} -- and
reads reliability off how often the votes concur. A third, recent line builds
multi-agent detectors whose agents specialize on different signals and whose
rationales are merged into a single explanation~\cite{phishdebate2025,
multiphishguard2025}. Together these families cover much of the space of accuracy
and aggregation.

\input{../figures/fig_teaser_qualitative}

They share a blind spot, visible in a routine case (\autoref{fig:teaser}). A page
impersonating a bank is shown to a panel of three diverse models; all three return
``phishing,'' so every aggregation method above reports high confidence. But the
models reached that verdict for different reasons: one cited the morphed logo, one
cited a credential form posting off-domain, and one cited a certificate mismatch
that does not actually hold on the page. First, the detectors emit a label and
discard these reasons, so nothing auditable reaches the operator (\limit{1}).
Second, reliability is read at the \emph{label}, where the three agree, and is
therefore blind to the fact that they \emph{disagree on the evidence}: the verdict
is right for the wrong reason (\limit{2}). Third, even where the models do agree on
a reason, that agreement can be a shared hallucination of a cue that is not on the
page (\limit{3}). A right-label, wrong-reason verdict is not a curiosity: it is
precisely the verdict a small change to the cited cue would flip, and precisely the
one an operator should not act on blindly.

Two properties of phishing, not shared by generic question answering, make a
direct remedy possible. First, the evidence a detector relies on is
\emph{objectively checkable}: a form-action domain, a certificate organization, a
redirect target, and a rendered logo can each be re-derived from the page itself.
Second, labeled pages are cheap to assemble -- public feeds publish freshly
confirmed phishing URLs and legitimate sites supply benign pages -- so a detector's
operating point can be set on a held-out labeled split rather than guessed. The evidence that decides a verdict is also
\emph{heterogeneous}, spanning several model types (text LLMs and a
vision-language model), many signals (URL, DOM, certificate, redirect chain, logo,
and credential intent), two modalities, and a verification mechanism per signal.
Deciding which signals to gather for a given page and how to combine them is a
\emph{planning-and-aggregation} problem better suited to an agent than to a fixed
pipeline, and modern LLMs can act as such agents -- emitting typed outputs and
calling tools to gather and verify their own evidence. The opportunity is to stop
treating reliability as a property of labels and start treating it as a property of
\emph{evidence that several independent agents plan, gather, verify, and agree on,
and that the page confirms}.

To this end, we present \toolname, a multi-\emph{agent} phishing detector that
trusts a verdict in proportion to grounded cross-model agreement on the evidence.
A small, deliberately diverse panel of LLM \emph{evidence agents} investigates the
page: rather than emit a bare label, each agent \emph{plans} which signals and
modalities to examine, then gathers and grounds its evidence by calling
verification \emph{tools} -- a DOM parser, a certificate reader, a redirect tracer,
a logo matcher, and an existing reference-based or LLM brand detector -- and records
what it found in a shared, per-page set of typed \emph{evidence cues}, each carrying
the asserting agent and the confirming tool. \toolname{} \emph{aggregates} these
grounded findings: it measures agreement at the level of the cited \emph{evidence}
rather than the label, weights that agreement by whether each agreed cue verifies
against the page, and combines the two into a single Grounded Evidence-Agreement (GEA)
score. It acts only when the score is high -- returning the agreed, verified cues as
a checkable explanation -- and otherwise abstains, escalating the page to deeper
analysis or a human. A calibrator fit on a held-out labeled split maps the score to
a probability of correctness, so the operating point is set against real outcomes
rather than guessed. Reusing the existing detectors as tools also makes \toolname{}
able to match or exceed specialized detectors on full-coverage accuracy by construction,
since the panel inherits their signal. The novelty over prior multi-agent detectors is the unit of
agreement: not the label, and not one model's introspective faithfulness, but a set
of evidence cues that is simultaneously cross-agent-agreed and tool-verified.

Realizing this raises three difficulties that the design must rule out. First, to
answer \limit{2}, agreement over structured evidence must be defined so that it
cannot collapse into label agreement in disguise -- two models can name the same
brand while resting on entirely different cues. Second, to answer \limit{3}, shared hallucination must be caught
cheaply, by checking cited cues against the page rather than trusting the models to
police themselves. Cutting across both, the panel must stay small: every added
agent is another round of model and tool calls, so the gain has to come from agent
\emph{diversity} rather than count.

We make the following contributions.
\begin{compactitem}
\item \textbf{Failure mode.} We identify the \emph{right-label, wrong-reason}
failure of multi-model phishing detectors and cast trustworthy detection as
selective prediction over an evidence-agreement signal (\autoref{sec:formulation}).
\item \textbf{Method.} We introduce \toolname{}, a panel of tool-using evidence
agents that cite a shared set of typed, verified evidence cues, and its Grounded
Evidence-Agreement score, which measures cross-agent agreement over those cues and
turns it, calibrated on a held-out labeled split, into a selective act/abstain
decision with the agreed, verified cues as the explanation (\autoref{sec:method}).
\item \textbf{Evidence.} On a phishing benchmark of feed-sourced phishing pages paired
with legitimate login pages, \toolname{} matches or exceeds the re-run specialized
detectors (D1 Phishpedia, D3 PhishLLM) on full-coverage F1 while improving the
risk--coverage trade-off over single-model confidence and label voting:
it has, by a clear and statistically significant margin, the lowest expected calibration
error of any method ($0.015$) and the highest selective accuracy at $80\%$ coverage
($97.0\%$), so its reported probability of correctness can be acted on directly; its area under the risk--coverage curve (AURC) is
the lowest in point estimate ($38\%$ below the label-agreement baseline) though within the
confidence interval (CI) of the strongest baseline (\autoref{sec:experiments}).
\item \textbf{Analysis.} We isolate the contribution of evidence-level agreement,
tool-grounding, agent diversity, and calibration; cross-family \emph{diversity} and
calibration are the dominant factors, while on this benchmark -- where phishing pages
carry an unambiguous off-brand signal and few shared hallucinations -- grounding adds
little to the ranking and the right-label-wrong-reason effect is modest, appearing only
on the harder lookalike pages (\autoref{sec:experiments}, \autoref{sec:limitations}).
Under evidence-targeted attack, however, grounding earns its place: occluding the brand
logo collapses groundedness and the detector abstains, while a single-model confidence
baseline stays maximally confident on the now-wrong verdict, and the fail-safe holds even
against a white-box adversary that corrupts every cited cue at once (\autoref{sec:exp_adv}).
We further show the calibrated trust transfers to brands unseen during calibration
(\autoref{sec:exp_brands}), and that the parameter-free, small-model design is not beaten by a
learned aggregator or a $2$--$3\times$ larger panel -- the bottleneck is evidence elicitation,
not model scale (\autoref{sec:exp_negatives}).
\end{compactitem}

The rest of the paper is organized as follows. \autoref{sec:related} positions
\toolname{} against label-level reliability and multi-agent detection.
\autoref{sec:formulation} formalizes grounded evidence-agreement and the selective
objective. \autoref{sec:method} details the evidence agents, the cues they cite, the score,
and the calibrated decision rule, and
\autoref{sec:experiments} reports the evaluation.
